GPU-Beschleunigung der Material Point Method

### 2018-11-17 mscthesis.tex
apic paper starts now

@@

  =  \int _ { \Omega ^ { t } } \frac{\partial _tq _ { i }}{\partial _tx_k} ( _t\boldsymbol { x } , t )\sigma _ {ik} d_t\boldsymbol{x}

@@

  = \int _ { \partial \Omega ^ { t } } _tq _ { i } ( _t\boldsymbol { x } , t ) \sigma _ {ij} d_tA_t\boldsymbol{x} -  \int _ { \Omega ^ { t } } \frac{\partial _tq _ { i }}{\partial _tx_k} ( _t\boldsymbol { x } , t )\sigma _ {ik} d_t\boldsymbol{x}.

@@

>>>>

  d_0\boldsymbol{x}.

@@

  =  \int _ { \Omega ^ { t } } \frac{\partial _tq _ { i }}{\partial _tx_k} ( _t\boldsymbol { x } , t )\sigma _ {ik} d_t\boldsymbol{x}.

@@

  = \int _ { \partial \Omega ^ { t } } _tq _ { i } ( _t\boldsymbol { x } , t ) \sigma _ {ij} d_tA_j(_t\boldsymbol{x}) -  \int _ { \Omega ^ { t } } \frac{\partial _tq _ { i }}{\partial _tx_k} ( _t\boldsymbol { x } , t )\sigma _ {ik} d_t\boldsymbol{x}.

@@

\subsection{Material Particles}
  w( x ) = \left\{ \begin{array} { l l } { \frac { 1 } { 2 } | x | ^ { 3 } - | x | ^ { 2 } + \frac { 2 } { 3 } } & { 0 \leqslant | x | < 1 } \\ { \frac { 1 } { 6 } ( 2 - | x | ) ^ { 3 } } & { 1 \leqslant | x | < 2 } \\ { 0 } & { 2 \leqslant | x | } \end{array} \right.
  \nabla w_{\boldsymbol{i}}(\boldsymbol{x})
  =\frac { 1 } {  { h } }
  \left(
    \begin{array} {l}
      w^{\prime} (\frac { 1 } {  { h } } ( x  - x _ { i } ))  { w }          ( \frac { 1 } {  { h } } (  { y }  -  { y } _ { i}  ) )   { w }         ( \frac { 1 } {  { h } } ( z  - z _ { i } ) \\
      w(\frac{1} {  { h } } ( x  - x _ { i } ))               { w }^{\prime} ( \frac { 1 } {  { h } } (  { y }  -  { y } _ { i}  ) )   { w }         ( \frac { 1 } {  { h } } ( z  - z _ { i } ) \\
      w(\frac{1} {  { h } } ( x  - x _ { i } ))               { w }          ( \frac { 1 } {  { h } } (  { y }  -  { y } _ { i}  ) )   { w }^{\prime}( \frac { 1 } {  { h } } ( z  - z _ { i } ) \\
    \end{array}
  \right)
